Reproducible Validation and Replication Studies in Nanoscale Physics

### 2020-09-05 tex/ClementiBarba2020.tex
fix different PyGBe writings, replace all for /pygbe
add Rockstuhl to acknowledgements

%%%% Abstract text to be placed here %%%%%%%%%%%%
\begin{abstract}
    Credibility building activities in computational research include
    verification and validation, reproducibility and replication, and
    uncertainty quantification. Though orthogonal to each other, they are
    related. This paper presents validation and replication studies in 
    electromagnetic excitations on nanoscale structures, where the quantity
    of interest is the wavelength at which resonance peaks occur. 
    The study uses the open-source software PyGBe: a boundary element
    solver with treecode acceleration and GPU capability.
    We replicate a result by Rockstuhl et al. (2005, doi:10/dsxw9d) with a
    two-dimensional boundary element method on silicon carbide particles,
    despite differences in our method. 
    The second replication case from Ellis et al. (2016, doi:10/f83zcb) looks
    at aspect ratio effects on high-order modes of localized surface phonon-polariton
    nanostructures. The results partially replicate: the wavenumber
    position of some modes match, but for other modes they differ.
    With virtually no information about the original simulations, 
    explaining the discrepancies is not possible. 
    A comparison with experiments that measured polarized reflectance 
    of silicon carbide nano pillars provides a validation case.
    The wavenumber of the dominant mode and two more do match, but 
    differences remain in other minor modes. 
    Results in this paper were produced with strict reproducibility
    practices, and we share reproducibility packages for all, including
    input files, execution scripts, secondary data, post-processing code and
    plotting scripts, and the figures (deposited in Zenodo).
    In view of the many challenges faced, we propose that reproducible
    practices make replication and validation more feasible.

@@

We thank Dr. Chase T. Ellis  and Dr. Joseph G. Tischler for the fruitful discussions regarding their results \cite{ellis2016}, 
which led to the validation of \pygbe, and for providing a mesh file and dielectric data that made the modeling closer to their original setup.
We also thank Dr. Christopher D. Cooper for many valuable discussions that helped us overcome some of the challenges faced throughout this work.

>>>>

%%%% Abstract text to be placed here %%%%%%%%%%%%
\begin{abstract}
    Credibility building activities in computational research include
    verification and validation, reproducibility and replication, and
    uncertainty quantification. Though orthogonal to each other, they are
    related. This paper presents validation and replication studies in 
    electromagnetic excitations on nanoscale structures, where the quantity
    of interest is the wavelength at which resonance peaks occur. 
    The study uses the open-source software \pygbe: a boundary element
    solver with treecode acceleration and GPU capability.
    We replicate a result by Rockstuhl et al. (2005, doi:10/dsxw9d) with a
    two-dimensional boundary element method on silicon carbide particles,
    despite differences in our method. 
    The second replication case from Ellis et al. (2016, doi:10/f83zcb) looks
    at aspect ratio effects on high-order modes of localized surface phonon-polariton
    nanostructures. The results partially replicate: the wavenumber
    position of some modes match, but for other modes they differ.
    With virtually no information about the original simulations, 
    explaining the discrepancies is not possible. 
    A comparison with experiments that measured polarized reflectance 
    of silicon carbide nano pillars provides a validation case.
    The wavenumber of the dominant mode and two more do match, but 
    differences remain in other minor modes. 
    Results in this paper were produced with strict reproducibility
    practices, and we share reproducibility packages for all, including
    input files, execution scripts, secondary data, post-processing code and
    plotting scripts, and the figures (deposited in Zenodo).
    In view of the many challenges faced, we propose that reproducible
    practices make replication and validation more feasible.

@@

We thank Dr. Chase T. Ellis  and Dr. Joseph G. Tischler for the fruitful discussions regarding their results \cite{ellis2016}, 
which led to the validation of \pygbe, and for providing a mesh file and dielectric data that made the modeling closer to their original setup.
We also thank Dr. Christopher D. Cooper for many valuable discussions that helped us overcome some of the challenges faced throughout this work. 
After we posted the preprint on arXiv (just after submission to the journal), we received communication from Prof. Dr. Carsten Rockstuhl that helped us clarify some points in our paper, which we appreciate.
